### 2025-01-05 sections/1-introduction.tex
wip: changes by NI
reference fixes

Many researchers are interested in similarity search on these datasets.
Similarity search enables a variety of applications, including recommendation~\cite{annoy} and classification systems~\cite{suyanto2022knnclassifier}.
As the cardinalities and dimensionalities of datasets have grown, however, efficient and accurate similarity search has become challenging;
even state-of-the-art algorithms exhibit a steep tradeoff between recall and throughput~\cite{Malkov2016EfficientAR, johnson2019billion, annoy, aumuller2020ann}.

@@

>>>>

Many researchers are interested in similarity search on these datasets.
Similarity search enables a variety of applications, including recommendation~\cite{annoy} and classification systems~\cite{suyanto2022knnclassifier}.
As the cardinalities and dimensionalities of datasets have grown, however, efficient and accurate similarity search has become challenging;
even state-of-the-art algorithms exhibit a steep tradeoff between recall and throughput~\cite{malkov2016hnsw, johnson2019billion, annoy, aumuller2020ann}.

@@

\subsection{Entropy Scaling Search}
\label{sec:intoduction:entropy-scaling-search}
